A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-13 bioc-workflow.Rmd
replication: what about correlation? ; fix also bug in code

The more relevant comparison unit is not a single fraction, but rather
the complete protein occupancy profiles, which are best visualised as
experiment-wide on a PCA plot. As such, we prefer to focus on the
direct, qualitative comparison of individual replicate PCA plots,
assuring that each displays acceptable sub-cellular resolution. Note
that in the code chunk below, we mirror the y-axis to represent the
two figures with the same orientation.

```{r plot2Drep, fig.width = 12}
par(mfrow = c(1, 2))
plot2D(hl[hl$replicate == 1], fcol = "SVM.marker.set", main = "Replicate 1")
plot2D(hl[hl$replicate == 2], fcol = "SVM.marker.set", main = "Replicate 2",
       mirrorY = TRUE)
```

>>>>

The more relevant comparison unit is not a single fraction, but rather
the complete protein occupancy profiles, which are best visualised as
experiment-wide on a PCA plot. As such, we prefer to focus on the
direct, qualitative comparison of individual replicate PCA plots,
assuring that each displays acceptable sub-cellular resolution. Note
that in the code chunk below, we mirror the x-axis to represent the
two figures with the same orientation.

```{r plot2Drep, fig.width = 12}
par(mfrow = c(1, 2))
plot2D(hl[, hl$replicate == 1], fcol = "SVM.marker.set", main = "Replicate 1")
plot2D(hl[, hl$replicate == 2], fcol = "SVM.marker.set", main = "Replicate 2",
       mirrorX = TRUE)
```

Peason correlation

```{r}
i1 <- exprs(hl[, hl$replicate == 1])
i2 <- exprs(hl[, hl$replicate == 2])
pearcor <- cor(t(i1), t(i2))
mean(diag(pearcor))
```

- What about classification on different replicates?
